\documentclass[a4paper,10pt]{article}
%-----------------------------------------------------------
% {{{
\usepackage[top=0.75in, bottom=0.75in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{url}
\usepackage{palatino}
\usepackage{multirow}
\fontfamily{SansSerif}
\selectfont

\usepackage[T1]{fontenc}
\usepackage[ansinew]{inputenc}
% \usepackage{helvetica}
% \usepackage{array}
\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=10in
\raggedbottom
% \raggedright
\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.5cm}
\renewcommand{\labelitemii}{$\circ$}
% Adjust margins
%\addtolength{\oddsidemargin}{-0.375in}
%\addtolength{\evensidemargin}{-0.375in}
%\addtolength{\textwidth}{1.75in}
%\addtolength{\topmargin}{0.1375in}
%\addtolength{\textheight}{1.75in}
\pagestyle{empty}
% }}}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small
        {
            \begin{minipage}
                {0.975\textwidth}\textbf{{\textsc{#1 \vphantom{p\^{E}} }}}
                \\[-0.3cm]
                \hrule
            \end{minipage}
            \\[-0.5cm]
        }
 }}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r}
    \textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}
% \textit{#3} &  \\
%-----------------------------------------------------------

\begin{document}
{{{
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\[-0.3cm]
}}}

% \indent \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lr}
% \multirow{3}{*}{\huge\textsc{\textbf{Abhijeet Dubey}}}	& \textbf{Email:} \href{mailto:dubey.abhijeet09@gmail.com}{dubey.abhijeet09@gmail.com}				\\
% 							& \textbf{Website:} \href{https://github.com/dracarys09/}{github.com/dracarys09/}	\\
% 							& \textbf{Phone:} +91 9900190105
% \end{tabular*}

% % \resheading{\textbf{\large Areas of Interest}}\\[\lsep] \\[-0.4cm]
% % %{{{
% %     \begin{itemize}
% %     \item[] 
% %     \hspace{-0.4cm} $\bullet$ Machine Learning 
% %     \hspace{0.2cm} $\bullet$ Natural Language Processing
% %   \hspace{0.2cm} $\bullet$ Algorithms
% % \end{itemize}
% %}}}

% {\textbf{\large{ACADEMIC DETAILS}}}\\[\lsep]
% \\[0.2cm]
% \indent \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}cccc}
% \hline
% \textbf{Degree}	&	\textbf{University}			&	\textbf{Year}	&	\textbf{CPI / \%}	\\
% \hline
% Post Graduation	&	IIT Bombay			&  2019	& 7.8 / 10		\\[0.15cm]
% Graduation	&	IIIT Jabalpur	& 2016	& 8.4 / 10		\\[0.15cm]
% Intermediate/+2		&	CBSE				&  2012	 &	92.2 \%		\\[0.15cm]
% Matriculation		&	CBSE					& 2010	&	9.2/10		\\
% \hline
% \end{tabular*}
% \\ \\

\resheading{\textbf{\large WORK EXPERIENCE}}\\[\lsep] \\[-0.4cm]
% {{{
\begin{itemize}
\item \textbf{Google Summer of Code}  \\
    \emph{Software Development Internship, The Linux Foundation} \hfill {\emph{(May 2017 - Aug 2017)}}
    \\[-0.6cm]
    \begin{itemize}
        \item Implemented a backend module (Google Cloud Print (GCP) Back-end) by wrapping Google Cloud Print API for Common Printing Dialog project under The Linux Foundation.
        \item The aim of this project was to provide unified printing from all applications on all available printers via all technologies that a user is using.
        \item GCP backend provides support for cloud ready printers which facilitate printing on Google Cloud Printers remotely.
    \end{itemize}

\item \textbf{Oracle Corporation} \\
    \emph{Software Development Internship}
    \hfill {\emph{(Jun 2015 - Nov 2015)}}
    \\ [-0.6cm]
      \begin{itemize}\itemsep \isep
        \item Designed and implemented a test suite to perform Smoke Testing of Oracle's SIM Software.
        \item Used Keyword based tabular testing tool Synergy to develop robust test suite and improved the overall coverage.
    \\ [-0.6cm]
      \end{itemize}

\item \textbf{Uddhat Softwares Pvt. Ltd.} \\
    \emph{Web Development Internship} \hfill {\emph{(Jun 2014 - Jul 2014)}}
    \\ [-0.6cm]
    \begin{itemize}\itemsep \isep
    \item Developed an online marketplace enabling freelancers to offer their services to users.
    \end{itemize}
\end{itemize}

% }}}

\resheading{\textbf{\large MASTER's THESIS \& RESEARCH PROJECTS}}\\[\lsep]
\\[-0.4cm]
%{{{
\begin{itemize}

\item \textbf{ Deep Models for Computational Sarcasm Detection \& Interpretation} \\ \emph{(Master's Thesis, Guided by Prof. Pushpak Bhattacharyya \& Dr. Aditya Joshi (CSIRO, Sydney))}
    \\ [-0.6cm]
    \begin{itemize}\itemsep \isep
    \item Conducted a literature survey on various state of the art models for computational sarcasm detection and interpretation.
    \item Explored a specific type of sarcasm which arises due to numbers and implemented an Attention Network for detecting sarcasm due to numbers in tweets. This model performed significantly better than existing state of the art models and obtained a precision of \textbf{0.91}, recall of \textbf{0.92} and F-Score of \textbf{0.91}.
    \item Future work involves modelling additional context in the form of richer user embeddings to enhance the performance of sarcasm detection systems.
    \end{itemize}

\item \textbf{Sarcasm Interpretation}
\\ {\emph{(R\&D Project, Guided by Prof. Pushpak Bhattacharyya \& Dr. Aditya Joshi (CSIRO, Sydney))}}
    \\ [-0.6cm]
    \begin{itemize}\itemsep \isep
    \item Modelled sarcasm interpretation task as a monolingual machine translation problem.
    \item Implemented Sarcasm-SIGN algorithm using Moses for converting sarcastic utterances into their non sarcastic interpretation and obtained a BLEU score of \textbf{67.96}.
    \item Implemented a rule based approach by modelling sarcasm as a theory of dropped negation and obtained a BLEU score of \textbf{50.56}.

    \end{itemize}

\end{itemize}

\resheading{\textbf{\large SCHOLASTIC ACHIEVEMENTS}}\\[\lsep]
\begin{itemize}\itemsep \isep
    \item Qualified for \textbf{ACM ICPC} Amritapuri Onsite Regionals in 2015.
    \item Awarded \textbf{Certificate of Merit} two times for exceptional academic performance during freshmen year and sophomore year.
    \item Was among top \textbf{0.3\%} in GATE Computer Science 2016 among 1.08 lakh candidates.
    \item \textbf{$1^{st}$} place in Obfuscated 2015 (programming competition).
    \item \textbf{Won Bronze Medal} in National Round of iURL, held at IIT Bombay in March 2014.
\end{itemize}

\pagebreak
\resheading{\textbf{\large ACADEMIC PROJECTS}}\\[\lsep]
\\[-0.4cm]
%{{{
\begin{itemize}

\item \textbf{ Headline Prediction from News Articles} \\ \emph{(CS726: Advanced Machine Learning, Prof. Sunita Sarawagi)}
    \\ [-0.6cm]
    \begin{itemize}\itemsep \isep
    \item Implemented LSTM Network with Attention and trained our network on parallel corpora of news articles and their headlines.
    \item Used state of the art models like Google\mbox{'}s Pointer Generator Network and Facebook\mbox{'}s NAMAS.
    \item Best results were produced by Pointer Generator Network which produced a BLEU score of \textbf{31.3}.
    \end{itemize}

\item \textbf{Intelligent Carrom Playing Agent}
\\ {\emph{(CS747: Foundations of Intelligent \& Learning Agents, Prof. Shivaram Kalyanakrishnan)}}
    \\ [-0.6cm]
    \begin{itemize}\itemsep \isep
    \item Implemented two models, Continuous Actor-Critic based agent and Deterministic Agent that can play carrom in both single player and 2 player setting.
    \item Best performing agent was able to clear the carrom board within \textbf{23} turns on average in single player mode.

    \end{itemize}


\item \textbf{Music Generation Using LSTM}
\\ {\emph{(CS753: Automatic Speech Recognition, Prof. Preethi Jyothi)}}
    \\ [-0.6cm]
    \begin{itemize}\itemsep \isep
    \item Implemented LSTM model to synthesize music frames for Piano and Electronic Dance Music (EDM).
    \item Compared results of LSTM model with note based music synthesis and raw waveform based music synthesis models.
    \end{itemize}


\item \textbf{Music Genre Classification}
\\ {\emph{(CS725: Foundations of Machine Learning, Prof. Ganesh Ramakrishnan)}}
    \\ [-0.6cm]
    \begin{itemize}\itemsep \isep
    \item Used classifiers like Decision Tree, Random Forests and Neural Network to classify music genres.
    \item Achieved \textbf{63.5\%} accuracy using timbral features which was an improvement of \textbf{2.5\%} over the original GTZAN Music Genre Classification Paper.
    \end{itemize}
    
\item \textbf{Low Cost Solution for Car Heating Problem}
\\ {\emph{(Fabrication Project, Prof. Saket Saurav)}}
    \\ [-0.6cm]
    \begin{itemize}\itemsep \isep
    \item A solar powered hot air exhaust system for commercial vehicles.
    \item A miniature device that triggers an exhaust system depending on the internal car temperature when car is idle.
    \end{itemize}

\end{itemize}
\vspace{0.1cm}
\hspace{0.5cm}\resheading{\textbf{\large Technical Skills}}
\begin{itemize}
  \item \textbf{Programming Languages}: C, C++, Python, PHP, HTML, CSS, Javascript \\[-0.6cm]
  \item \textbf{Tools \& Frameworks}: Git, \LaTeX, Beamer, Keras, PyTorch, Laravel, Django, Ansible\\[-0.6cm]
\end{itemize}\\[\lsep] \\
\\[-0.8cm]
%{{{
%}}}
\vspace{0.2cm}
\hspace{0.4cm} \resheading{\textbf{\large Positions of Responsibility}}\\[\lsep] \\[-0.4cm]
%{{{
\begin{itemize}
    \item \textbf{Research Assistantship, IIT Bombay }\emph{(under Prof. D.B.Phatak)}\hfill {\emph{(Jul 2016-Present)}} \\[-0.6cm]
        \begin{itemize}
                \item Responsible for mentoring a group of summer interns during May'17-Jul'17 and May'18-Jul'18.
                \item Responsible for writing deployment scripts of Collaborative Communities Portal using Ansible.
                \item Part of the interview panel and interviewed candidates for selection into Master's Program in IIT Bombay.
        \end{itemize}
    \item \textbf{Student Companion }\emph{(ISCP, IIT Bombay)}\hfill {\emph{(Jul 2017-Jun 2018)}} \\[-0.6cm]
        \begin{itemize}
                \item Mentored a group of five students by providing continuous help and support on both academic and non-academic fronts.
        \end{itemize}
    \item \textbf{Assistant Coordinator }\emph{(Student Counselling Services, IIIT Jabalpur)}\hfill {\emph{(Aug 2014-July 2015)}} \\[-0.6cm]
        \begin{itemize}
                \item Mentored a group of 5 undergraduate students during their sophomore year.
        \end{itemize}
    \item \textbf{Student Guide }\emph{(Student Counselling Services, IIIT Jabalpur)}\hfill {\emph{(Aug 2013-Jul 2014)}} \\[-0.6cm]
        \begin{itemize}
                \item Mentored a group of 5 undergraduate students during their freshmen year.
        \end{itemize}
\end{itemize}
%}}}


% \resheading{\textbf{\large RELEVANT COURSEWORK} }\\[\lsep]
% % \vspace{0.2cm}
% \begin{itemize}
% \item Foundations of Machine Learning, Advanced Machine Learning, Intelligent \& Learning Agents, Automatic Speech Recognition, Artificial Intelligence, Algorithms \& Complexity. 
% \end{itemize}



\vspace{0.1cm}
\resheading{\textbf{ \large INTERESTS AND HOBBIES} }\\[\lsep]
\begin{itemize}
\item \noindent Weigtlifting, World Cinema, Playing Guitar.
\end{itemize}


\end{document}

